### 2021-01-28 input/proposal.tex
more on dynamic networks

Joining the network is equivalent to add as many communication links
as necessary between the joining process and its new neighbors.

\paragraph{Dynamic networks with dynamic partitions.}
When removing a communication link between two processes does not
break any active path, because neither distances of processes depend
on the other, then nothing needs to be done. \NAME have no overhead.
Unfortunately, when a process' distance depends on the other process,
the protocol becomes much more complex. Indeed, this requires to
\TODO{undo} all add messages originated from this process. \TODO{Why
  distance is not sufficient ?} \TODO{Why not use this from the first
  step then, or why other steps are still relevant?}

\paragraph{A last optimisation}

\TODO{Carry information that is useless. such as order of processes in
  paths, and identities of processes themselves.}

@@

\TODO{To rework, for there are more components now.}

>>>>

\noindent Joining the network is equivalent to add as many
communication links as necessary between the joining process and its
new neighbors.

\paragraph{Dynamic networks with dynamic partitions.}
When removing a communication link between two processes does not
break any active path, because neither distances of processes depend
on the other, then nothing needs to be done. \NAME has no overhead.
Unfortunately, when a process' distance depends on the other process,
the protocol becomes much more complex. Indeed, this requires to
\TODO{undo} all add messages originated from this process. A message
must convey the fact that
\begin{inparaenum}[(i)]
\item an edge at a particular process has been removed, and
\item the distance that has been delivered by a process comes from
  this particular process.
\end{inparaenum}

\noindent \NAME handles this as a particular case of partition within
current partition: it contains to affected regions the traffic
generated to patch affected regions. In order to know if it is
affected by the \TODO{undo} operation, using distances already
piggybacked in messages is not sufficient.  Each process must know the
path taken by delivered message. Since we do not beforehand which
communication links will crash and which messages will be affected by
undos, each message has to carry its path along forwarding. This also
allows processes to remove loops, for they cannot rely on version
number (that remains unchanged) for this operation.

\noindent Instead of version number, one could use such paths to remove loops
due to \TODO{add and del}, however this may be much more costly in
terms of generated traffic. Version numbers guarantee that only one
delete is delivered and all prior inserts are then discarded, while
using paths, processes may deliver multiple inserts and deletes before
reaching termination. \TODO{maybe clearer with figures.} As
consequence, \NAME still makes use of vector of versions.

\noindent Although costly, piggybacking paths with logical partitioning synergies
well, for the size of these paths decreases quickly as the number of
partitions grows.

\paragraph{A last optimisation}
\TODO{Carry information that is useless. such as order of processes in
  paths, and identities of processes themselves.} \TODO{Icarus for
  dissemination trees~\cite{whitaker2002forwarding}}. \TODO{No need to
  know the dimension of networks and
  partitions~\cite{almeida2007scalable}}.

@@

\TODO{To rework, for there are more components now. Maybe do this
  along the description of the approach.}
